High-order cognition is supported by complex but compressible brain activity patterns

### 2023-03-01 paper/main.tex
backing up progress on discussion section

other themes:
- predictability implies redundancy

>>>>

Correlations or causal associations between different brain regions
simultaneously imply that full-brain activity patterns will be compressible and
also that those activity patterns will contain redundancies. For example, the
extent that activity patterns at one brain area can be inferred or predicted
from activity patterns at other areas~\citep[e.g.,][]{OwenEtal20, ScanEtal21},
reflects overlap in the information available in or represented by those brain
areas. If brain patterns in one area are recoverable using brain patterns in
another area, then the ``signal'' used to convey the activity patterns could be
compressed by removing the recoverable activity. Predictable (and therefore
redundant) brain activity patterns are also more robust to signal corruption.
For example, even if the activity patterns at one region are unreadable or
unreliable at a given moment, that unreliability could be compensated for by
other region's activity patterns that are predictive of the unreliable region.

other themes:
